---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# EnrichMe

<!-- badges: start -->
<!-- badges: end -->

The goal of EnrichMe is to to perform GSEA on a ranked list of objects and set
    of objects as genes.  The second method to test association between
    gene set and ranked list of objects is to retrieve the leading-edge
    subset and then perform a Fisher's exact test.  It also gives the
    possibility to automatically search set of genes from different
    database from the web.  Finally, it gives some functions to visualize
    the result of GSEA.

## Installation

You can install the development version of EnrichMe like so:

``` r
devtools::install_local("path/to/tar.gz")

#For the get_web_sets function, you need to download extra packages #from Bioconductior with the BiocManager package (already present #in the dependency) 
missing.pkgs <- c("AnnotationDbi","GO.db","ReactomePA","KEGGREST","org.Hs.eg.db","reactome.db")
BiocManager::install(missing.pkgs, update=FALSE)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, warning=FALSE}
library(EnrichMe)

data("gaf_file")
data("gmt_file")
#If you have your own set lists
sets <- read_set_gmt(gmt_file)
str(sets)
#Is using gaf format
sets <- read_set_gaf(gaf_file, "C")
str(sets)
#If you have no sets
sets <- get_web_sets()
str(sets)

data("ranked.list")
data("fatty_acid_metabolism")
#If you want to enrich one particular set
res <- one_set_analysis(ranked.list, fatty_acid_metabolism, n.perm = 1000)
res

#If you want to enrich multiple sets
data("pathways")
res <- multiple_set_analysis(ranked.list, pathways, n.perm = 1000)
res[1:10,]

#To visualize the multiple set analysis
dotplot(res)
```
